Multi-objective autotuning of MobileNets\\ across the full software/hardware stack

### 2018-06-12 dissemination.publication/08da9685582866a0/paper_appendix.tex
Update appendix.

\begin{packed_itemize}
  \item {\bf Algorithm:} image classification
  \item {\bf Program:} MobileNets using Arm Compute Library v17.12+ and TensorFlow 1.7.0+
  \item {\bf Compilation:} GCC v6+ (recommended v7+); Python 2.7+ or 3.4+
  \item {\bf Transformations:}
  \item {\bf Binary:} compiled from source on a target platform
  \item {\bf Data set:} ImageNet 2012 validation (50,000 images)
  \item {\bf Run-time environment:} Linux; OpenCL v1.2+
  \item {\bf Hardware:} Linaro HiKey960, Firefly RK3399 development boards (or similar)
  \item {\bf Run-time state:} CPU and GPU frequencies set to the maximum
  \item {\bf Execution:} 
  \item {\bf Metrics:} total execution time; top1/top5 accuracy over some (all) images from the data set
  \item {\bf Output:} classification result; execution time (throughput/latency) versus accuracy
  \item {\bf Experiments:} automated via CK command line
  \item {\bf How much disk space required (approximately)?} 4..20GB depending on library installations
  \item {\bf How much time is needed to prepare workflow (approximately)?} from 30 minutes to 1 day (if natively building TF)
  \item {\bf How much time is needed to complete experiments (approximately)?} from 30 minutes to 1 week (if validating accuracy on complete data set)
  \item {\bf Publicly available?:} Yes
  \item {\bf Code license(s)?:} BSD 3-clause
  \item {\bf CK workflow framework used?} Yes
  \item {\bf CK workflow URL:} \url{https://github.com/dividiti/ck-request-asplos18-mobilenets-armcl-opencl}
  \item {\bf CK results URL:} \url{https://github.com/ctuning/ck-request-asplos18-results-mobilenets-armcl-opencl}
\end{packed_itemize}

@@

\textbf{NB:} Execute commands prefixed with `\#` sign under `root` or using `sudo`.

First, install CK workflow framework:

@@

Alternatively, you can install latest CK version in a user space from GitHub:
\begin{verbatim}
$ git clone http://github.com/ctuning/ck
$ export PATH=$PWD/ck/bin:$PATH
$ export PYTHONPATH=$PWD/ck:$PYTHONPATH
\end{verbatim}

\noindent Then, install CK repositories:
\begin{verbatim}
$ ck pull repo --url=https://github.com/dividiti/ck-request-asplos18-mobilenets-armcl-opencl
$ ck pull repo:ck-tensorflow
\end{verbatim}

@@

Software dependencies for CK workflows are automatically installed and rebuilt 
via shared CK packages: \url{https://github.com/ctuning/ck/wiki/Shared-packages}.

However, they may still require some native packages:

@@

\begin{verbatim}
$ ck install package \
  --tags=mobilenet-v1-all,tensorflowmodel,2017_06_14 
\end{verbatim}

@@

\begin{verbatim}
$ ck install package:lib-armcl-opencl-request
$ ck install package:lib-armcl-opencl-18.03 \
  --env.USE_GRAPH=ON --env.USE_NEON=ON
\end{verbatim}

@@

\begin{verbatim}
$ ck install package:lib-tensorflow-1.7.0-src-cpu \
  --env.CK_HOST_CPU_NUMBER_OF_PROCESSORS=1
\end{verbatim}

@@

We suggest to check the ReadME from the live CK workflow 
for the latest installation and usage instructions:

\url{https://github.com/dividiti/ck-request-asplos18-mobilenets-armcl-opencl} .

>>>>

\begin{packed_itemize}
  \item {\bf Algorithm:} image classification
  \item {\bf Program:} MobileNets using Arm Compute Library v17.12+ and TensorFlow 1.7.0+
  \item {\bf Compilation:} GCC v6+ (recommended v7+); Python 2.7+ or 3.4+
  \item {\bf Transformations:}
  \item {\bf Binary:} compiled from source on a target platform
  \item {\bf Data set:} ImageNet 2012 validation (50,000 images)
  \item {\bf Run-time environment:} Linux; OpenCL v1.2+
  \item {\bf Hardware:} Linaro HiKey960, Firefly RK3399 development boards (or similar)
  \item {\bf Run-time state:} CPU and GPU frequencies set to the maximum
  \item {\bf Execution:} 
  \item {\bf Metrics:} total execution time; top1/top5 accuracy over some (all) images from the data set
  \item {\bf Output:} classification result; execution time (throughput/latency) versus accuracy
  \item {\bf Experiments:} automated via CK command line
  \item {\bf How much disk space required (approximately)?} 4..20GB depending on library installations
  \item {\bf How much time is needed to prepare workflow (approximately)?} from 30 minutes to 1 day (if natively building TensorFlow)
  \item {\bf How much time is needed to complete experiments (approximately)?} from 30 minutes to 1 week (if validating accuracy on the full ImageNet validation data set of 50,000 images)
  \item {\bf Publicly available?:} Yes
  \item {\bf Code license(s)?:} BSD 3-clause
  \item {\bf CK workflow framework used?} Yes
  \item {\bf CK workflow URL:} \url{https://github.com/dividiti/ck-request-asplos18-mobilenets-armcl-opencl}
  \item {\bf CK results URL:} \url{https://github.com/ctuning/ck-request-asplos18-results-mobilenets-armcl-opencl}
\end{packed_itemize}

@@

\textbf{NB:} Execute commands prefixed with `\#' sign under the `root' account or with `sudo'.

First, install the Collective Knowledge framework (CK):

@@

Alternatively, you can install the latest CK version from GitHub in the user space:
\begin{verbatim}
$ git clone http://github.com/ctuning/ck
$ export PATH=$PWD/ck/bin:$PATH
$ export PYTHONPATH=$PWD/ck:$PYTHONPATH
\end{verbatim}

\noindent Then, install the required CK repositories:
\begin{verbatim}
$ ck pull repo --url=https://github.com/dividiti/ck-request-asplos18-mobilenets-armcl-opencl
\end{verbatim}

\subsubsection{Install this CK workflow from the ACM Digital Library snapshot}

You can install and test a snapshot of this workflow 
from the ACM Digital Library without interfering with your current CK installation.
Download related file {\tt request-asplos18-artifact-?-ck-workflow.zip}
to a temporary directory, unzip it and then execute the following commands:

\begin{verbatim}
$ . ./prepare_virtual_ck.sh
$ . ./start_virtual_ck.sh
\end{verbatim}

All the required CK repositories will be installed in your current directory.
%You can now proceed with further evaluation as described below.

@@

Software dependencies for CK workflows are automatically installed and rebuilt 
via shared CK packages.\footnote{\url{https://github.com/ctuning/ck/wiki/Shared-packages}}
However, they may still require some native packages:

@@

\begin{verbatim}
$ ck install package --tags=mobilenet-v1-all,tensorflowmodel,2017_06_14 
\end{verbatim}

@@

\begin{verbatim}
$ ck install package:lib-armcl-opencl-request
$ ck install package:lib-armcl-opencl-18.03 --env.USE_GRAPH=ON --env.USE_NEON=ON
\end{verbatim}

@@

\begin{verbatim}
$ ck install package:lib-tensorflow-1.7.0-src-cpu --env.CK_HOST_CPU_NUMBER_OF_PROCESSORS=1
\end{verbatim}

@@

We recommend to check {\tt README} from the live CK workflow for the latest
installation and usage instructions:

\url{https://github.com/dividiti/ck-request-asplos18-mobilenets-armcl-opencl}
